Approximation as Differentiation

### 2025-07-08 main/approx-as-tangents.tex
Typos.

We end this section with a conjecture. Although we have argued above
that there is an analogy between stable functions and smooth
functions, we have not stated any mathematical theorems substantiating
this. \emph{Tangent Categories} \cite{tangent-categories} are a
categorical axiomatisation of the properties of manifolds and smooth
functions in terms of the presence of tangent bundles $TX$ for every
object $X$, forward derivatives and additivity of tangents. They
generalise Cartesian Differential Categories \cite{cdcs}, which are an
axiomatisation of Euclidean spaces and smooth functions.

>>>>

We end this section with a conjecture. Although we have argued above
that there is an analogy between stable functions and smooth
functions, we have not stated any mathematical theorems substantiating
this. \emph{Tangent Categories} \cite{cockett14,cockett18} are a
categorical axiomatisation of the properties of manifolds and smooth
functions in terms of the presence of tangent bundles $TX$ for every
object $X$, forward derivatives and additivity of tangents. They
generalise Cartesian Differential Categories \cite{cdcs}, which are an
axiomatisation of Euclidean spaces and smooth functions.

### 2025-07-08 main/models.tex
Typos.

In the case of $\FinVect$, the solution is to expand to the category
of all vector spaces $\Vect$, where infinite direct products
exist. Note that these infinite products are not biproducts because
the vector space operations themselves are finitary. This is the
solution that \cite{vakar2021} uses for the semantics of forward
($\Fam(\Vect)$) and reverse ($\Fam(\Vect^\op)$) automatic
differentiation for higher order programs. Since the forward and
reverse derivatives of a smooth map intrinsically defined,
\citet{vakar2021}'s correctness theorem shows that, for programs with
first-order type, the interpretation in $\Fam(\Vect)$ correctly yields
the forward derivative of the defined function on the reals (and
reverse derivative for $\Fam(\Vect^\op)$.

>>>>

In the case of $\FinVect$, the solution is to expand to the category
of all vector spaces $\Vect$, where infinite direct products
exist. Note that these infinite products are not biproducts because
the vector space operations themselves are finitary. This is the
solution that \cite{vakar2021} uses for the semantics of forward
($\Fam(\Vect)$) and reverse ($\Fam(\Vect^\op)$) automatic
differentiation for higher order programs. Since the forward and
reverse derivatives of a smooth map are intrinsically defined,
\citet{vakar2021}'s correctness theorem shows that, for programs with
first-order type, the interpretation in $\Fam(\Vect)$ correctly yields
the forward derivative of the defined function on the reals (and
reverse derivative for $\Fam(\Vect^\op)$).
